% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Dean Johnson}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{318 NW 12th St}
 \moveleft.5\hoffset\centerline{Corvallis, OR 97330}
 \moveleft.5\hoffset\centerline{(503) 470-9217}
 \moveleft.5\hoffset\centerline{Github: github.com/johnsdea}


\begin{resume}
 
\section{EDUCATION} B.S. Computer Science, Oregon State University - Expected 2015
                    \begin{itemize}  \itemsep -2pt %reduce space between items
                     \item GPA: 3.11 
                    \end{itemize}

\section{SKILLS} {\sl Languages:} 
                    \begin{itemize}  \itemsep -2pt %reduce space between items
                     \item Proficient: Python 
                     \item Familiar: Java, C++, C, {Html}, Javascript
                    \end{itemize}
                {\sl Frameworks \& Libraries: } 
                    \begin{itemize}  \itemsep -2pt %reduce space between items
                    \item Flask, Django, Selenium, Celery, SQLAlchemy
                    \end{itemize}
                {\sl Other: }
                    \begin{itemize}  \itemsep -2pt %reduce space between items
                    \item Unix, Git, Vagrant
                    \end{itemize}
 
\section{EXPERIENCE} 
                \textbf{Student Developer} \hfill June 2012 - Present \\
                OSU Open Source Lab, Corvallis OR \\
                {\sl ORVSD Central} 
                \begin{itemize}  \itemsep -2pt %reduce space between items
                    \item A Flask application for managing Moodle sites, and doing remote course installations.
                          Database interaction is handled via SQLAlchemy, course installations are done asynchronously 
                          with celery.
                    \item Project manager and lead developer.
                \end{itemize}
                \textbf{Introduction to Programming T.A.}  \hfill January 2013 - Present  \\
                Oregon State University, Corvallis OR
                \begin{itemize}  \itemsep -2pt %reduce space between items
                \item Helped design pieces of the curriculum for incoming Computer Science students.
                \item Lead labs and answered questions for students.
                \item Graded student assignments based on correctness and completeness.
                \end{itemize} 
                \textbf {Intel Open Source Company} \hfill September 2011 - June 2012 \\
                Oregon State University, Corvallis OR 
                   \begin{itemize} \itemsep -2pt
                    \item Project manager for group focused on genetic algorithm applied toward structural design.
                    \end{itemize} 
  
\section{PERSONAL PROJECTS \&\\ AWARDS}
            Flatter Me Please ({\sl flattermeplease.com})
            \begin{itemize} \itemsep -2pt
                \item A web application for brightening someone else's day through
                    personalized compliments.
                \item Award from OSU Application Hackathon for "Largest (Potential) User Base."
                \item github.com/johnsdea/flatterer
            \end{itemize}
            Textbook Exchange ({\sl txtbookexchange.com})
            \begin{itemize} \itemsep -2pt
                \item A web application to help college students buy/sell textbooks locally.
                    I had trouble finding books using the Facebook groups at Oregon State, 
                    so I wrote the app to help students running into the same issues. The app is
                    written using Flask, and utilizes an API for book information autocompletion.
                \item github.com/johnsdea/txtbookexchange
            \end{itemize}

\end{resume}
\end{document}
